%% /clear page, 
\clearpage
\section{Problem: Real Estate Portfolio Optimization Problem}


Quantum computing can optimize $2^n$ combinations through $n$ qubits by giving 1(select) or 0(reject). Therefore, the binary variable selection method can be excellently applied to fields that optimize portfolios, such as stocks. Various quantum-based companies such as IBM, Multiverse, and QCWare are currently stepping up their portfolio optimization projects. Of course, when quantum computers are developed, algorithm trading will be possible, considering countless companies' stock prices and market conditions. However, generating and applying such algorithms at the current level is impossible.

Therefore, the real estate market in Korea is the area where quantum computers can be most efficiently applied to the portfolio optimization sector through NISQ (Noisy Intermediate-Scale Quantum) currently. In fact, according to the paper(?????) , the Korean real estate market shares very similar characteristics to the stock market. Unlike the stock market, where transactions are possible up to the decimal point, real estate is a unique asset that exists only one at a time, so it is suitable to express as a binary form. In addition, budget constraints are currently impossible when optimizing portfolios.  investment advisors and asset managers can raise the amount of capital they want to form a portfolio with real estate, so they can be free from budget constraints.








%% /clear page, 
\clearpage